Corpus Experiments for Word Embeddings

### 2015-08-25 article/main.tex
don't sub VOID vec in coocc noise exp heatmap; fix figure refs

\textcolor{red}{what about some work introducing tokens into a corpus for experiments?}
\textcolor{red}{cite ``contextual distinctiveness: a new lexical property ...'' by McDonald and Shillcock?}

@@

\begin{table}\label{word-occurrences-table}
	\input{words-occurrences.tex}
	\caption{ Number of words, by frequency band, as observed in the unmodified corpus.  }
\end{table}

@@

\begin{table}\label{word-frequency-counts}
	\input{word-frequency-experiment-counts.tex}
	\caption{Occurrence counts for words chosen for the word frequency experiment. }
\end{table}

\begin{figure}\label{fig:word-frequency-experiment-text-cat}
	\begin{mdframed}
	\input{word-frequency-experiment-text-cat.tex}
	\end{mdframed}
	\caption{A text modified for the word frequency experiment as per subsection \ref{WFVEexisting}, where the
	word \word{cat} was chosen, $\lambda=0.5$ and $n=20$.}
\end{figure}

@@

\begin{figure}\label{fig:word-frequency-experiment-text-void}
	\begin{mdframed}
	\input{word-frequency-experiment-text-void.tex}
	\end{mdframed}
	\caption{A text modified for the word frequency experiment as per subsection \ref{WFVEmeaningless}, where $\lambda=0.5$ and $n=20$. For illustrative purposes, the token \word{VOID} was here interspersed with a global frequency of $0.05$.}
\end{figure}
\end{subsection}

@@

\begin{figure}\label{word-frequency-experiment-heatmap}
	\includegraphics[scale=0.5]{word-frequency-experiment-heatmap}
	\caption{
	Heatmap of the cosine similarity of the vectors associated to the
	tokens introduced into the corpus in the co-occurrence noise experiment
	(words other than \word{the} and \word{VOID} chosen randomly).
	}
\end{figure}

\begin{table}\label{word-frequency-experiment-cosine-similarity}
	\input{cosine-similarity.tex}
	\caption{
	The most similar words in the original vocabulary to the tokens
	introduced into the corpus associated to the word \word{the},
	and their cosine similarity with the most frequent such token,
	\word{THE\_1}.  It is apparent from the nearest neigbours that
	the word vectors of the low frequency tokens have not been
	adequately trained (there were inadequate samples).
	}
\end{table}

\begin{sidewaysfigure*}\label{fig:word-frequency-experiment-graph}
	\centering{\includegraphics[scale=0.6]{word-frequency-experiment-graph}}
	\caption{
	Vector length vs frequency for the words chosen for the word frequency
	experiment.  For each word, tokens of varying frequency but with the
	co-occurrence distribution of that word were introduced into the
	corpus, as described in section \ref{WFVE}.
	The word vectors are obtained from the first synaptic layer, ``syn0''.
	The second layer ``syn1neg'' is included for completeness.
	}
\end{sidewaysfigure*}

@@

\begin{table}\label{cooccurrence-noise-words}
	\input{noise-cooccurrence-experiment-counts.tex}
	\label{fig:co-occurrence-noise-counts}
	\caption{Occurrence counts for words chosen for the co-occurrence noise experiment. }
\end{table}

@@

\begin{figure}\label{fig:co-occurrence-noise-heatmap}
	\includegraphics[scale=0.5]{cooccurrence-noise-heatmap}
	\caption{
	Heatmap of the cosine similarity of some of the vectors associated to the
	tokens introduced into the corpus in the co-occurrence noise experiment
	(four such words chosen at random).  The
	largely red blocks demonstrate that the direction of the word vector
	does not change when noise is added to the co-occurrence distribution.
	}
\end{figure}

\begin{sidewaysfigure*}\label{fig:co-occurrence-noise-graph}
	\includegraphics[scale=0.6]{cooccurrence-noise-graph}
	\caption{
	Vector length vs proportion of co-occurrence noise for words
	chosen for the co-occurrence noise experiment.  For each word,
	tokens of equal frequency but with increasing proportions of
	co-occurrence noise were introduced into the corpus, as
	described in section \ref{CNVE}.
	The word vectors are obtained from the first synaptic layer, ``syn0''.
	The second layer ``syn1neg'' is included for completeness.
	}
\end{sidewaysfigure*}

>>>>

\textcolor{red}{what about some work introducing tokens into a corpus for experiments?}

\textcolor{red}{cite ``contextual distinctiveness: a new lexical property ...'' by McDonald and Shillcock?}

@@

\begin{table}
	\input{words-occurrences.tex}
	\caption{ Number of words, by frequency band, as observed in the unmodified corpus.  }
	\label{word-occurrences-table}
\end{table}

@@

\begin{table}
	\input{word-frequency-experiment-counts.tex}
	\caption{Occurrence counts for words chosen for the word frequency experiment. }
	\label{word-frequency-counts}
\end{table}

\begin{figure}
	\begin{mdframed}
	\input{word-frequency-experiment-text-cat.tex}
	\end{mdframed}
	\caption{A text modified for the word frequency experiment as per subsection \ref{WFVEexisting}, where the
	word \word{cat} was chosen, $\lambda=0.5$ and $n=20$.}
	\label{fig:word-frequency-experiment-text-cat}
\end{figure}

@@

\begin{figure}
	\begin{mdframed}
	\input{word-frequency-experiment-text-void.tex}
	\end{mdframed}
	\caption{A text modified for the word frequency experiment as per subsection \ref{WFVEmeaningless}, where $\lambda=0.5$ and $n=20$. For illustrative purposes, the token \word{VOID} was here interspersed with a global frequency of $0.05$.}
	\label{fig:word-frequency-experiment-text-void}
\end{figure}
\end{subsection}

@@

\begin{figure}
	\includegraphics[scale=0.5]{word-frequency-experiment-heatmap}
	\caption{
	Heatmap of the cosine similarity of the vectors associated to the
	tokens introduced into the corpus in the co-occurrence noise experiment
	(words other than \word{the} and \word{VOID} chosen randomly).
	}
	\label{word-frequency-experiment-heatmap}
\end{figure}

\begin{table}
	\input{cosine-similarity.tex}
	\caption{
	The most similar words in the original vocabulary to the tokens
	introduced into the corpus associated to the word \word{the},
	and their cosine similarity with the most frequent such token,
	\word{THE\_1}.  It is apparent from the nearest neigbours that
	the word vectors of the low frequency tokens have not been
	adequately trained (there were inadequate samples).
	}
	\label{word-frequency-experiment-cosine-similarity}
\end{table}

\begin{sidewaysfigure*}
	\centering{\includegraphics[scale=0.6]{word-frequency-experiment-graph}}
	\caption{
	Vector length vs frequency for the words chosen for the word frequency
	experiment.  For each word, tokens of varying frequency but with the
	co-occurrence distribution of that word were introduced into the
	corpus, as described in section \ref{WFVE}.
	The word vectors are obtained from the first synaptic layer, ``syn0''.
	The second layer ``syn1neg'' is included for completeness.
	}
	\label{fig:word-frequency-experiment-graph}
\end{sidewaysfigure*}

@@

\begin{table}
	\input{noise-cooccurrence-experiment-counts.tex}
	\label{fig:co-occurrence-noise-counts}
	\caption{Occurrence counts for words chosen for the co-occurrence noise experiment. }
	\label{cooccurrence-noise-words}
\end{table}

@@

\begin{figure}
	\includegraphics[scale=0.5]{cooccurrence-noise-heatmap}
	\caption{
	Heatmap of the cosine similarity of some of the vectors associated to the
	tokens introduced into the corpus in the co-occurrence noise experiment
	(four such words chosen at random).  The
	largely red blocks demonstrate that the direction of the word vector
	does not change when noise is added to the co-occurrence distribution.
	}
	\label{fig:co-occurrence-noise-heatmap}
\end{figure}

\begin{sidewaysfigure*}
	\includegraphics[scale=0.6]{cooccurrence-noise-graph}
	\caption{
	Vector length vs proportion of co-occurrence noise for words
	chosen for the co-occurrence noise experiment.  For each word,
	tokens of equal frequency but with increasing proportions of
	co-occurrence noise were introduced into the corpus, as
	described in section \ref{CNVE}.
	The word vectors are obtained from the first synaptic layer, ``syn0''.
	The second layer ``syn1neg'' is included for completeness.
	}
	\label{fig:co-occurrence-noise-graph}
\end{sidewaysfigure*}
